---
title: "CKD-EPI 2009 Creatinine vs CKD-EPI 2021 Creatinine"
format: html
embed-resources: true
params:
  df: NULL
  ckdepi2009cr_egfr: NULL
  ckdepi2021cr_egfr: NULL
  ckdepi2009cr_ckd_stages: NULL
  ckdepi2021cr_ckd_stages: NULL
---

```{r}
#| label: Loading Corner
#| include: false
library(ckdepicompare)
df <- readRDS(params$df)
```

# Bland-Altman Plot

This plot compares the estimated glomerular filtration rate (eGFR) values of patients derived from both the CKD-EPI 2009 Creatinine and the CKD-EPI 2021 Creatinine equations.

```{r}
#| label: Bland-Altman Plot
#| echo: false
baplotr::plot_ba(
  df = df,
  methodA = params$ckdepi2009cr_egfr,
  methodB = params$ckdepi2021cr_egfr,
  title = "CKD-EPI 2009 Creatinine vs CKD-EPI 2021 Creatinine",
  xlabel = "Mean of CKD-EPI 2009 Creatinine eGFR and CKD-EPI 2021 Creatinine eGFR",
  ylabel = "CKD-EPI 2009 Creatinine eGFR - CKD-EPI 2021 Creatinine eGFR"
)
```

# Reclassification Table

This table shows the amount of patients who has had their chronic kidney disease (CKD) staging changed after calculating their eGFR using the CKD-EPI 2021 Creatinine equation.

```{r}
#| label: Reclassification Table
#| echo: false
tbl <- reclass_table(
  df = df,
  ckdepi2009cr_ckdstage = params$ckdepi2009cr_ckd_stages,
  ckdepi2021cr_ckdstage = params$ckdepi2021cr_ckd_stages
)
kableExtra::kbl(tbl) |>
  kableExtra::add_header_above(c("CKD-EPI 2009 Cr" = 1, "CKD-EPI 2021 Cr"= 6), font_size = 11)
```
